### 2025-05-05 frontmatter/acknowledgements.tex
Pre-correction version of thesis

Finally, Wouter Waalejwin, who I met in the fourth year of my PhD, has been an incredibly patient mentor and a valuable resource for me in learning the ins and outs of quantum chromodynamics.
%
His presence is felt in many subtle ways throughout this thesis.
%
I can see his gentle, knowing smile even now.

@@

@@

My academic siblings have also been important parts of my journey, and have taught me and been with me through both trials and tribulations.
%
Sean Benevedes, who I have known since my time at UCSB, carries with him an intelligence, humor, and empathy that make world a measurably better place.
%
I have also benefited from many useful conversations with Rikab Gambhir, whose funny jokes, intelligence, and unimpeachable sense of academic adventure have made my experience at MIT much more interesting.
%
Last but not least, Cari Cesarotti is a hilarious, high-powered, creative scientist who I love to watch playing the game of science and winning.

@@

More of my academic family from UCSB who have had an incredible positive influence on my life are James Ehrets (I have learned and gained so much from his openness and adventurousness, empathy, and many long conversations), Nicholas O'Dea (who perhaps belongs in my ``mentor'' section: he has shaped my entire attitude towards learning and rigor), David Newsom (he knows the many odd and memorable adventures we have shared together -- what an incredible and interesting life), Jasmin Kwak (who is an unshakeable source of support whenever I need her), Ben Siegel (whose gentle kindness I always aspire to), Dolev Bluvstein (who is a damn superhuman -- I don't know how he does it, but I feel so lucky to learn from his incredible positivity and brilliant approach to all of life), Anoop Praturu, Ryan Stuart, and Marvin Qi.
%
My b-boy crew, including Kai Goh, Eugene Ma, Brandon Louie, and Alvin Ong have given me many adventures as well, along with companionship, growth, a beautiful and positive environment for my studies, and the incredible gift of \emph{art}.
%
Last, and perhaps most important, is Yurim Lee, who gave me so much kindness, supported me through

At MIT, I was lucky enough to meet even more incredible and brilliant people.
%
I'm very grateful to Zhiquan Sun, who taught me among many wonderful lessons that a happy life means eating well.
%
Another close friend is Christopher McNally, who is open to anything, saved my life in the wilderness on one occasion, and saved my spirit in and out of the halls of MIT many more.
%
Some of my first friends at MIT were Atakan Firat (a tireless dynamo of intellect and creativity who never backs down from a fight), Ouail Kitouni (humble beyond belief, whose openness and kindness are only emphasized by his incredible knowledge, curiosity, and problem-solving ability), Shankar Balasubramanian (a pure genius, plain and simple, always with time to teach, share a problem, or give advice), Margarita Davydova (a kind, creative, brilliant theorist who makes science as beautiful as art), Ali Ghorashi (always with support and empathy to share), and Anjie Gao (who taught me, among other things, the wisdom that ``nothing is trivial'').
%
Though it took one more semester, I soon met Patrick Oare, Wenzer Qin, Artur Avkadiev -- my moral support group -- who have since been my people:
%
my confidants, my comrades-in-arms, my rocks.
%
Nick Kamp and Caolan John also deserve a special mention here;
%
they bring positivity and curiosity into every room, and every room is better for their presence.
%
Nathan Everett (my platonic soul mate) and Lubah Lerner (his soul mate) have also been close friends and wonderful sources of joy and support.
%
I have been lucky enough to learn from and share time with Dimitra Pefkou, \r{A}smund Folkestad, Gregory Ridgway, Joshua Lin, Yitian Sun, Sarah Geller, Jamison Sloan, Robert Jones, Manu Srivastava, and Ankita Budhraja.
%
I especially want to thank Lisa Yang, whose constant drive for self-improvement is continually inspiring.

The entirety of the Engineering Quantum Systems (EQuS) ``chill team'' deserves a special mention for the joy they have brought to my life:
%
Sarah Muschinske, Miguel and Lean\'or Moreira, Jorge Marques, and Andreia Allen -- and also to Will Oliver, whose incredible positive and guiding influence has brought these wonderful, brilliant people together.  % TODO: fix Leanor if necessary
%
David Rower, Lamia Ateshian, and Dolev Bluvstein deserve more thanks here as well, and Marcin Kalinowski should be thanked three times (once for his wonderful personality, twice for his incredible science, and three times for his enormous muscles, which count as another person on their own).

>>>>

Finally, Wouter Waalewijn, who I met in the fourth year of my PhD, has been an incredibly patient mentor and a valuable resource for me in learning the ins and outs of quantum chromodynamics.
%
His presence is felt in many subtle ways throughout this thesis.
%
I can see his gentle, knowing smile even now.

@@

I am also extremely grateful for Paul Zeizel, who, along with his sharp wit and skill in listening, has the incredible talent of always saying the right thing.

@@

My academic siblings have also been important parts of my journey, and have taught me and been with me through both trials and tribulations.
%
Sean Benevedes, who I have known since my time at UCSB, carries with him an intelligence, humor, and empathy that make world a measurably better place.
%
I have also benefited from many useful conversations with Rikab Gambhir, whose funny jokes, intelligence, and unimpeachable sense of academic adventure have made my experience at MIT much more interesting.
%
I am grateful for many enthusiastic conversations about physics and life with Sokratis Trifinopoulos, and for being able to glimpse his creativity and his extremely honest positivity -- he speaks his mind even in disagreement, but somehow I always feel happier after talking with him than I had before.
%
Last but not least, Cari Cesarotti is a hilarious, high-powered, creative scientist who I love to watch playing the game of science and winning.

@@

More of my academic family from UCSB who have had an incredible positive influence on my life are James Ehrets (I have learned and gained so much from his openness and adventurousness, empathy, and many long conversations), Nicholas O'Dea (who perhaps belongs in my ``mentor'' section: he has shaped my entire attitude towards learning and rigor), David Newsom (he knows the many odd and memorable adventures we have shared together -- what an incredible and interesting life), Jasmin Kwak (who is an unshakeable source of support whenever I need her), Ben Siegel (whose gentle kindness I always aspire to), Dolev Bluvstein (who is a damn superhuman -- I don't know how he does it, but I feel so lucky to learn from his incredible positivity and brilliant approach to all of life), Anoop Praturu, Ryan Stuart, and Marvin Qi.
%
My b-boy crew, including Kai Goh, Eugene Ma, Brandon Louie, and Alvin Ong have given me many adventures as well, along with companionship, growth, a beautiful and positive environment for my studies, and the incredible gift of \emph{art}.
%
Yurim Lee gave me so much kindness and support through my studies at UCSB for which I am forever grateful.

At MIT, I was lucky enough to meet even more incredible and brilliant people.
%
I'm very grateful to Zhiquan Sun, who taught me among many wonderful lessons that a happy life means eating well.
%
Another close friend is Christopher McNally, who is open to anything, saved my life in the wilderness on one occasion, and saved my spirit in and out of the halls of MIT many more.
%
Some of my first friends at MIT were Atakan Firat (a tireless dynamo of intellect and creativity who never backs down from a fight), Ouail Kitouni (humble beyond belief, whose openness and kindness are only emphasized by his incredible knowledge, curiosity, and problem-solving ability), Shankar Balasubramanian (a pure genius, plain and simple, always with time to teach, share a problem, or give advice), Margarita Davydova (a kind, creative, brilliant theorist who makes science as beautiful as art), Ali Ghorashi (always with support and empathy to share), and Anjie Gao (who taught me, among other things, the wisdom that ``nothing is trivial'').
%
Though it took one more semester, I soon met Patrick Oare, Wenzer Qin, Artur Avkadiev -- my moral support group -- who have since been my people:
%
my confidants, my comrades-in-arms, my rocks.
%
Nick Kamp and Caolan John also deserve a special mention here;
%
they bring positivity and curiosity into every room, and every room is better for their presence.
%
Nathan Everett (my platonic soul mate) and Lubah Lerner (his soul mate) have also been close friends and wonderful sources of joy and support, as have Robbie Ball and Signe Wurtz.
%
I have been lucky enough to learn from and share time with Dimitra Pefkou, \r{A}smund Folkestad, Gregory Ridgway, Joshua Lin, Yitian Sun, Sarah Geller, Jamison Sloan, Robert Jones, Manu Srivastava, Kyle Lee, and Ankita Budhraja.
%
I especially want to thank Lisa Yang, whose constant drive for self-improvement is continually inspiring.

The entirety of the Engineering Quantum Systems (EQuS) ``chill team'' deserves a special mention for the joy they have brought to my life:
%
Sarah Muschinske, Miguel and Lean\'or Moreira, Jorge Marques, and Andreia Allen -- and also to Will Oliver, whose incredible positive and guiding influence has brought these wonderful, brilliant people together.
%
David Rower, Lamia Ateshian, and Dolev Bluvstein deserve more thanks here as well, and Marcin Kalinowski should be thanked three times (once for his wonderful personality, twice for his incredible science, and three times for his enormous muscles, which count as another person on their own).

### 2025-05-05 frontmatter/notation.tex
Pre-correction version of thesis

    \item
        The \glslink{splittingfn}{Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP) splitting functions}, computed in \Sec{splitting-functions} and related to the \glslink{dglapeqn}{DGLAP equation} in \Sec{p2p-fragmentation}, are often written in the \emph{exclusive} form \(P_{i\,j \leftarrow \ell}(z)\), with a probabilistic interpretation related to the probability of a parton of type \(\ell\) to split into partons of type \(i\), carrying an energy fraction \(z = z_i = E_i / E_\ell\), and type \(j\), carrying an energy fraction of \(z_j = 1-z\).
        %
        The \emph{inclusive} (meaning ``including a sum over some final state information'') DGLAP splitting functions are defined by
        \begin{align}
            \sum_{k'} P_{i\,k' \leftarrow \ell}(z) =: p_{i\leftarrow \ell}(z)
            \,.
        \end{align}

>>>>

    \item
        The \glslink{splittingfn}{Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP) splitting functions}, computed in \Sec{splitting-functions} and related to the \glslink{dglapeqn}{DGLAP equation} in \Sec{p2p-fragmentation}, are sometimes written in the \emph{exclusive} form \(P_{i\,j \leftarrow \ell}(z)\), with a probabilistic interpretation related to the probability of a parton of type \(\ell\) to split into partons of type \(i\), carrying an energy fraction \(z = z_i = E_i / E_\ell\), and type \(j\), carrying an energy fraction of \(z_j = 1-z\).
        %
        The \emph{inclusive} (meaning ``including a sum over some final state information'') DGLAP splitting functions are defined by
        \begin{align}
            \sum_{k'} P_{i\,k' \leftarrow \ell}(z) =: p_{i\leftarrow \ell}(z)
            \,.
        \end{align}

### 2025-05-05 frontmatter/preface.tex
Pre-correction version of thesis

\epigraph{You earn your right to speculate depending on how much work you do.}{Barton Zweibach}

@@

Second, since I attempt to provide especially clear and step-by-step derivations which highlight at least my own assumptions, several of the derivations presented in this thesis, even of fundamental concepts, are original.
%
Therefore, invoking the uncertainty principle, I advise you to watch closely for their \emph{correctness}.
%
I hope to have given enough detail to make this possible, and I encourage you to email me if I have not.

Finally, in addition to the several texts that appear in my citations below, another under-celebrated text on \glslink{qcd}{quantum chromodynamics} is \underline{Applications of Perturbative QCD}, by Richard D. Field \cite{Field:1989uq}, which pays incredible attention to detail in the presentation of calculations.
%
Of course, it would be a shame to access this book quickly, easily, and for free using \url{libgen.is}, so I will mention that it is also available (at time of writing) at \href{https://www.desy.de/~jung/qcd_and_mc_2009-2010/R.Field-Applications-of-pQCD.pdf}{this desy.de link}.

>>>>

\epigraph{You earn your right to speculate depending on how much work you do.}{Barton Zwiebach}

@@

Second, since I attempt to provide especially clear and step-by-step derivations which highlight at least my own assumptions, several of the derivations presented in this thesis, even of fundamental concepts, are original.
%
Though their conclusions are backed by history, I invoke the uncertainty principle, and advise you to watch closely for their \emph{correctness}.
%
I hope to have given enough detail to make this possible, and I encourage you to email me if I have not.
%
The framework I derive has definite limitations, including (but not limited to):
\begin{itemize}
    \item
        There is no formal discussion of the ``accuracy'' of our computations -- we simply take the soft- and collinear-limits as often as we must to make progress;

    \item
        There is no systematic regularization of infrared divergences;
\end{itemize}
I would be delighted to hear if you know of any places where my discussion is lacking.

Finally, in addition to the several texts that appear in my citations below, another under-celebrated text on \glslink{qcd}{quantum chromodynamics} is \underline{Applications of Perturbative QCD}, by Richard D. Field \cite{Field:1989uq}, which pays incredible attention to detail in the presentation of calculations.
%
Of course, it would be a shame to access this book quickly, easily, and for free using \url{libgen.is}, so I will mention that it is also available (at time of writing) at \href{https://www.desy.de/~jung/qcd_and_mc_2009-2010/R.Field-Applications-of-pQCD.pdf}{\texttt{this desy.de link}}.

### 2025-05-05 frontmatter/submission_information.tex
Pre-correction version of thesis

\begin{center}
    ~
    \vspace{50pt}

    {\LARGE \textbf{Particles Inside Particles:} }

@@

    \vspace{30pt}

    by

    \vspace{25pt}

    Samuel Alipour-fard

    \vspace{40pt}
    % \hrule
    \vspace{40pt}

    Submitted to the Department of Physics in partial fulfillment of the requirements for the degree of

@@

    DOCTOR OF PHILOSOPHY

    \vspace{15pt}

@@

    \vspace{15pt}

    MASSACHUSETTS INSTITUTE OF TECHNOLOGY

@@

    \vspace{40pt}
    % \hrule
    \vspace{40pt}

    \copyright{} 2025 Samuel Alipour-fard. All rights reserved.

\end{center}

>>>>

\begin{center}
    {\LARGE \textbf{Particles Inside Particles:} }

@@

    \vspace{20pt}
    \hruledotted{Submitted}{7.1cm}

    \vspace{-30pt}
    \begin{flushright}
        Samuel Alipour-fard
    \end{flushright}

    {\large to the Department of Physics in partial fulfillment of the requirements for the degree}

@@

    \textsc{Doctor of Philosophy}  % DOCTOR OF PHILOSOPHY

    \vspace{5pt}

@@

    \textsc{Massachusetts Institute of Technology}  % MASSACHUSETTS INSTITUTE OF TECHNOLOGY

@@

    {\large \copyright{} 2025 Samuel Alipour-fard. All rights reserved.}
\end{center}

### 2025-05-05 includes/glossary.tex
Pre-correction version of thesis

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thesis Glossary
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \providecommand{\myglsindextext}[1]{\glsentrydesc{#1} (\glsentrytext{#1})}
% \providecommand{\myglsindex}[1]{\index{\myglsindextext{#1}}}
% \providecommand{\mygls}[1]{\gls{#1}\myglsindex{#1}}
% \providecommand{\myglspl}[1]{\glspl{#1}\myglsindex{#1}}
% \providecommand{\myGls}[1]{\Gls{#1}\myglsindex{#1}}
% \providecommand{\myGlspl}[1]{\Glspl{#1}\myglsindex{#1}}

% TODO: run `makeglossaries thesis' whenever I want to redo the glossary

@@

%    \newglossaryentry{betafunction}
%    {
%        name=beta function (\ensuremath{\beta}),
%        text=beta function,
%        description={%
%            A function describing how the effective strength of QCD scattering changes with the energy of the scattered particles.
%            %
%            Not to be confused with the Euler beta function
%        },
%        parent=alphas
%    }

%    \newglossaryentry{frozencoup}
%    {
%      name=frozen coupling,
%      description={
%          A phenomenological prescription for modelling non-perturbative effects, in which the effective value of \(\alpha_s\) is fixed below an appropriately chosen non-perturbative scale
%      },
%      parent=alphas
%    }

% \newglossaryentry{betafunctioncoefficient}
% {
%     name=\ensuremath{\beta_k},
%     description={
%     }
% }

%\newglossaryentry{beta-sd}
%{
%    name=\ensuremath{\beta_\text{SD}},
%    description={
%        A parameter controlling the angular dependence of the \glsxshort{sd} algorithm.
%        %
%        As \(beta_\text{SD}\) gets larger, SD is more and more biased to remove wide-angle radiation;
%    }
%}

% \newglossaryentry{as}
% {
%   name=\ensuremath{a_s},
%   description={
%   A parameterization of the strong coupling \ensuremath{a_s = }\gls{alphas}\ensuremath{/4\pi} often emerging from loop calculations.
% },
% }

%\newglossaryentry{fsoft}
%{
%    name=\ensuremath{f_{\text{soft}}},
%    description={%
%        The fraction of the jet energy that is removed by \glsxshort{rsf}.
%        %
%        % The \gls{rsf} algorithm is described in \Section~\ref{sec:rsf}.
%    }
%}

@@

\newglossaryentry{elastic}
{
    name=elastic,
    text=elastic scattering,
    description={
    },
    parent=scattering
}

\newglossaryentry{inelastic}
{
    name=inelastic,
    text=inelastic scattering,
    description={
    },
    parent=scattering
}

@@

\newglossaryentry{vetoalg}
{
    name=algorithm,
    text=veto algorithm,
    description={
        \sam{link to sudakov factor/exponent?}
    },
    parent=veto
}
\newglossaryentry{vetoreg}
{
    name=region,
    text=veto region,
    description={
        \sam{link to radiator?}
    },
    parent=veto
}

>>>>

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thesis Glossary
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

\newglossaryentry{veto-algorithm}
{
    name=algorithm,
    text=veto algorithm,
    description={
        \sam{link to sudakov factor/exponent?}
    },
    parent=veto
}
\newglossaryentry{vetoreg}
{
    name=region,
    text=veto region,
    description={
        \sam{link to radiator?}
    },
    parent=veto
}
